working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-13 Manuscript_draft/Manuscript_draft.Rmd
adding effect size of phylo to draft

Add also plot with fruit production and pot it in appendix.Also the plots of ratios to appendices.

@@

@@

>>>>

Also the plots of ratios to appendices.

NMDS to appendix?

@@

[add table with morphometrical traits to appendix]()

@@

```{r, echo=FALSE, message=FALSE,warning=FALSE,cache=FALSE,fig.cap="Phylogenetic signal of the average heterospecific pollen effect size per species"}
library(ape)
library(phylosignal)
library(adephylo)
library(phylobase)
library(phylosignal)
library(caret)
library(ggplot2)
library(seqHMM)
library(dplyr)
library(reshape2)
pollen_tree=read.tree("Data/pollen_tree_no_outgroup.nwk")
effect_size_all <- readRDS( "Data/effect_size_all.RData")
#Now rename species
rownames(effect_size_all) <- c("Solanum_melongena","Solanum_lycopersicum","Petunia_integrifolia", "Capsicum_annuum","Ipomoea_purpurea","Ipomoea_aquatica","Sinapis_alba","Eruca_vesicaria","Brassica_rapa", "Brassica_oleracea")
hp_mean_sp=effect_size_all[,-c(1,3,4)]
p4d <- phylo4d(pollen_tree, hp_mean_sp)
barplot.phylo4d(p4d, center = TRUE , scale = FALSE,trait.labels="Hp effect",bar.col = c(rep("#0072B2",4), rep("#009E73",2), rep("#D55E00",4)))
```
